paper_pdf

### 2020-03-21 paper_pdf.Rmd
Changed some comments and cleaned up analysis.

### Data Preparation
Initially, there are 3140 observations. However, we decide to remove observations that contain null values for Percent eligibility for the Free Lunch Program. This reduces our observations to 3065. Before proceeding to model fitting, we will do some initial data exploration of our variables.

@@

Before we attempt with creating any more regression we should analyze the variables and make sure there is not too much data missing.

@@

After accounting for the missing values, we also want to know which variables are closely related to our two independent variables of ____ and _____. We can do this with a simple correlation heatmap.

@@

Thus we can see that we expect there to be a fairly strong positive correlation between Percent Eligibility of the Free Lunch Program with per capita WIC redemptions and SNAP benefits, as well all the poverty variables. Meanwhile when we analyze the Students eligible for Free Lunch Program per thousand variable, we can see that it is similarly correlated with the same variables. Thus we expect these variables to be significant in any regression we attempt.

## Linear Regression 
We will first attempt a linear regression with Percent of Students eligible for the Free Lunch Program as the dependent variable.

@@

### Goodness of fit: Hypothesis Test 
We want to test the hypothesis that the above model is more useful than a null model. We can let our null hypothesis be $$H_{0} : \text{Model with no independent variables fits data better than linear regression model}$$

@@

### Goodness of fit plots
It is important to analzye the assumptions of linear regression and see if our model meets them.

>>>>

### Data Preparation
Initially, there are 3140 observations. However, we decide to remove observations that contain null values for Percent eligibility for the Free Lunch Program, our dependent variable. This reduces our observations to 3065. Before proceeding to model fitting, we will do some initial data exploration of our variables.

@@

Based on the comparison of the two histograms, we decide to proceed with the first dependent and attempt a linear regression. Before we jump into regression we should analyze the variables and make sure there is not too much data missing.

@@

After accounting for the missing values, we also want to know which variables are closely related to Percent Eligibility of the Free Lunch Program. We can do this with a simple correlation heatmap.

@@

```
Thus we can see that we expect there to be a fairly strong positive correlation between Percent Eligibility of the Free Lunch Program with per capita WIC redemptions and SNAP benefits, as well all the poverty variables. Thus we expect these variables to be significant in our regressions.

## Model Fitting: Linear Regression 
We will attempt a linear regression with Percent of Students eligible for the Free Lunch Program as the dependent variable and the above variables listed as the independent variables.

@@

### Model Evaulation: Hypothesis Test 
We want to test the hypothesis that the above model is more useful than a null model. We can let our null hypothesis be $$H_{0} : \text{Model with no independent variables fits data better than linear regression model}$$

@@

### Model Evaluation: Goodness of fit plots
It is important to analzye the assumptions of linear regression and see if our model meets them.
